Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-14 Latex/sections/results.tex
removed weird english sentence; added 95%-üercentile error of uncorrected data
Added percentile table

Before the registration, the corridor is only represented acceptably in the front part. 
The further into the corridor, i.e., the longer the robot accumulates errors, the more imprecise the data becomes. 
Finally, we see that a large portion of the data even exceeds either the \SI{1}{\meter} error, contributing to the large spike in the histogram or even the \SI{2}{\meter} error limit; thus, being cut from the representation. 
After registration, we see that, qualitatively, the ideal corridor was nearly restored from the noisy data. 
In particular a very large portion (95\%) have less than \SI{17}{\centi\meter} distances.
Further, the square and straight shape of the corridor is restored well, and especially the large spike at errors of greater than \SI{1}{m} is removed. 
Any such errors tend to occur at the back and the front of the corridor where the measured range is the largest hence has the largest contribution of the range error.

>>>>

Before the registration, the corridor is only represented acceptably in the front part. 
The further into the corridor, i.e., the longer the robot accumulates errors, the more imprecise the data becomes. 
Finally, we see that a large portion of the data even exceeds either the \SI{1}{\meter} error, contributing to the large spike in the histogram or even the \SI{2}{\meter} error limit; thus, being cut from the representation. 
After registration, we see that, qualitatively, the ideal corridor was nearly restored from the noisy data. 
In particular a very large portion of points (95\%) have less than \SI{16.53}{\centi\meter} distances.
Table~\ref{tab:percentiles} shows the comparison of further percentiles of both datasets.

\begin{table}
	\centering
	\begin{tabular}{@{}cccc@{}}\hline
		& P90 & P95 & P98\\ \hline\hline
		Uncorrected & \SI{24.12}{\centi\meter} &  \SI{38.19}{\centi\meter} &  \SI{61.46}{\centi\meter}\\
		Corrected & \SI{12.78}{\centi\meter} &  \SI{16.53}{\centi\meter} &  \SI{21.55}{\centi\meter}\\ \hline
	\end{tabular}
	\caption{Comparison of percentiles of point-distances in the uncorrected and corrected simulated dataset.}
	\label{tab:percentiles}
\end{table}

Further, the square and straight shape of the corridor is restored well, and especially the large spike at errors of greater than \SI{1}{m} is removed. 
Any such errors tend to occur at the back and the front of the corridor where the measured range is the largest hence has the largest contribution of the range error.
